### 2022-12-14 paper1.tex
formatting and reproducibility

\subsection{The golden level}\label{sec1:goldenthresh}
Significance of both the original and the replication study at level $\alpha$ is
a necessary but not sufficient requirement for replication success at the
nominal level ($\alpha_S = \alpha$). The nominal level may therefore be too
stringent. It is more reasonable to calibrate the procedure in such a way that
to establish replication success, original and replication study do not both
necessarily need to be significant at level $\alpha$, provided that the
replication effect estimate does not shrink compared to the original one. We
therefore choose a level $\alpha_S$ such that a borderline significant original
study ($p_o = \alpha$) cannot lead to replication success if there is shrinkage
$s > 0$ of the replication effect estimate. Mathematically, this translates to
setting $\dinfty = 1$ and $K = z_\alpha^2/z_{\alpha_S}^2$
in~\eqref{eq1:smallestpossible} and leads to the quadratic equation $K(K-1) = 1$
with solution $K = \varphi$ where $\varphi = (\sqrt{5}+1)/2 \approx 1.62$ is
known as the golden ratio. Solving for $z_{\alpha_S}$ gives
$z_{\alpha_S} = z_\alpha / \sqrt{\varphi}$ and the corresponding \textit{golden
  level}
\begin{eqnarray}\label{eq1:golden}
\alpha_S & = & 1 -  \Phi(z_\alpha / \sqrt{\varphi} )
\end{eqnarray}
for replication success. This is our recommended default choice to assess
replication success and we will study its properties in the following in more
detail. For $z_\alpha = 1.96$ (one-sided $\alpha = 0.025$), the golden level is
$\alpha_S =0.062$. In the introductory example shown in Figure \ref{fig1:fig1},
the sceptical $p$-value is $p_S=0.11 > 0.062$, so the replication of the
\citet{Pyc2010} study was not successful.

The golden level \eqref{eq1:golden} is derived from~\eqref{eq1:smallestpossible}
with $\dinfty = 1$. However, we may also use a different value for the limiting
relative effect size $\dinfty$, say $\dinfty=0.8$. Then replication success is
only possible for a borderline significant result ($p_o = \alpha$) if there is
less than $1-\dinfty$ (20\% for $\dinfty=0.8$) shrinkage of the replication
effect estimate. This approach is equivalent to a limiting relative effect size
of 1 if the original $p$-value $p_o$ is equal to a different level $\alpha'$,
which can be derived as follows: First, solving \eqref{eq1:smallestpossible} for
$\dinfty > 0$ gives
$K = z_\alpha^2/z_{\alpha_S}^2 = 1/2+\sqrt{1/4 + 1/\dinfty^2}$. The new level
$\alpha'$ fulfills $\varphi=z_{\alpha'}^2/z_{\alpha_S}^2$, so
$z_\alpha^2/K=z_{\alpha'}^2/\varphi$ and therefore
\begin{equation}\label{eq1:alphaPrime}
\alpha' = 1-\Phi\left(z_{\alpha} \, \sqrt{\varphi / K} \right).
\end{equation}
For example, for $\alpha = 0.025$ and $\dinfty = 0.8$ we obtain $\alpha'=0.033$.

@@

The condition $p_S \leq \alpha_S$ for replication success at the golden level is
equivalent to $z_S \geq z_\alpha / \sqrt{\varphi}$, \ie{}
$z_S \sqrt{\varphi} \geq z_\alpha$. In practice it may be preferable to
recalibrate the sceptical $p$-value $p_{S} = 1 - \Phi(z_S)$ to
$ \tilde{p}_S = 1 - \Phi(z_S \sqrt{\varphi})$, which then needs to be compared
to $\alpha$ (rather than $\alpha_S$) to assess replication success and can thus
be interpreted on the same scale as an ordinary $p$-value. For example, the
recalibrated sceptical $p$-value for the replication of \citet{Pyc2010} turns
out to be $\tilde{p}_S=0.061$ and does not lead to replication success at any
level $\alpha<0.061$, including the standard $0.025$ level.

@@

The left plot in Figure \ref{fig1:fig4} displays the Type I error rate for
$\alpha=0.025$ as a function of the relative sample size $c$. It can be seen
that the Type I error of the replication success approach decreases with
increasing relative sample size $c$. This also follows from \eqref{eq1:T1E0}
where $\P(z_r \geq \zrmin \given z_o, c, \alpha_S) = 1 - \Phi(\zrmin)$ decreases
with increasing $c$, because $\zrmin$ increases with increasing $c$, see
equation \eqref{eq1:eq.z}.

@@

\section*{Data and Software}
Code and data to reproduce our analyses are available at
\url{https://github.com/SamCH93/RSgolden/}. A snapshot of the Git repository at
the time of writing is archived at \url{https://doi.org/10.5281/zenodo.XXXXXX}.
The data which was used is available in the R package
\texttt{ReplicationSuccess} (available on CRAN). Further information can be
found on the corresponding help page (with the command \texttt{?RProjects}).

\section*{Acknowledgments}
Support by the Swiss National Science Foundation (Project \#~189295) is
gratefully acknowledged. We acknowledge helpful and constructive comments by the
editor and a referee on an earlier version of this article.

>>>>

\subsection{The golden level}\label{sec1:goldenthresh}
Significance of both the original and the replication study at level $\alpha$ is
a necessary but not sufficient requirement for replication success at the
nominal level ($\alpha_S = \alpha$). The nominal level may therefore be too
stringent. It is more reasonable to calibrate the procedure in such a way that
to establish replication success, original and replication study do not both
necessarily need to be significant at level $\alpha$, provided that the
replication effect estimate does not shrink compared to the original one. We
therefore choose a level $\alpha_S$ such that a borderline significant original
study ($p_o = \alpha$) cannot lead to replication success if there is shrinkage
$s > 0$ of the replication effect estimate. Mathematically, this translates to
setting $\dinfty = 1$ and \mbox{$K = z_\alpha^2/z_{\alpha_S}^2$}
in~\eqref{eq1:smallestpossible} and leads to the quadratic equation $K(K-1) = 1$
with solution $K = \varphi$ where \mbox{$\varphi = (\sqrt{5}+1)/2 \approx 1.62$}
is known as the golden ratio. Solving for $z_{\alpha_S}$ gives
$z_{\alpha_S} = z_\alpha / \sqrt{\varphi}$ and the corresponding \textit{golden
  level}
\begin{eqnarray}\label{eq1:golden}
\alpha_S & = & 1 -  \Phi(z_\alpha / \sqrt{\varphi} )
\end{eqnarray}
for replication success. This is our recommended default choice to assess
replication success and we will study its properties in the following in more
detail. For $z_\alpha = 1.96$ (one-sided $\alpha = 0.025$), the golden level is
$\alpha_S =0.062$. In the introductory example shown in Figure \ref{fig1:fig1},
the sceptical $p$-value is $p_S=0.11 > 0.062$, so the replication of the
\citet{Pyc2010} study was not successful.

The golden level \eqref{eq1:golden} is derived from~\eqref{eq1:smallestpossible}
with $\dinfty = 1$. However, we may also use a different value for the limiting
relative effect size $\dinfty$, say $\dinfty=0.8$. Then replication success is
only possible for a borderline significant result ($p_o = \alpha$) if there is
less than $1-\dinfty$ (20\% for \mbox{$\dinfty=0.8$}) shrinkage of the
replication effect estimate. This approach is equivalent to a limiting relative
effect size of 1 if the original $p$-value $p_o$ is equal to a different level
$\alpha'$, which can be derived as follows: First, solving
\eqref{eq1:smallestpossible} for $\dinfty > 0$ gives
$K = z_\alpha^2/z_{\alpha_S}^2 = 1/2+\sqrt{1/4 + 1/\dinfty^2}$. The new
level~$\alpha'$ fulfills $\varphi=z_{\alpha'}^2/z_{\alpha_S}^2$, so
$z_\alpha^2/K=z_{\alpha'}^2/\varphi$ and therefore
\begin{equation}\label{eq1:alphaPrime}
\alpha' = 1-\Phi\left(z_{\alpha} \, \sqrt{\varphi / K} \right).
\end{equation}
For example, for $\alpha = 0.025$ and $\dinfty = 0.8$ we obtain $\alpha'=0.033$.

@@

The condition $p_S \leq \alpha_S$ for replication success at the golden level is
equivalent to $z_S \geq z_\alpha / \sqrt{\varphi}$, \ie{}
$z_S \sqrt{\varphi} \geq z_\alpha$. In practice it may be preferable to
recalibrate the sceptical $p$-value \mbox{$p_{S} = 1 - \Phi(z_S)$} to
$ \tilde{p}_S = 1 - \Phi(z_S \sqrt{\varphi})$, which then needs to be compared
to $\alpha$ (rather than $\alpha_S$) to assess replication success and can thus
be interpreted on the same scale as an ordinary $p$-value. For example, the
recalibrated sceptical $p$-value for the replication of \citet{Pyc2010} turns
out to be $\tilde{p}_S=0.061$ and does not lead to replication success at any
level $\alpha<0.061$, including the standard $0.025$ level.

@@

The left plot in Figure \ref{fig1:fig4} displays the Type I error rate for
$\alpha=0.025$ as a function of the relative sample size $c$. It can be seen
that the Type I error of the replication success approach decreases with
increasing relative sample size $c$. This also follows from \eqref{eq1:T1E0}
where \mbox{$\P(z_r \geq \zrmin \given z_o, c, \alpha_S) = 1 - \Phi(\zrmin)$}
decreases with increasing $c$, because $\zrmin$ increases with increasing $c$,
see equation \eqref{eq1:eq.z}.

@@

\section*{Data and Software}
Code and data to reproduce the analyses are available at
\url{https://github.com/SamCH93/RSgolden/}. A snapshot of the Git repository at
the time of writing is archived at \url{https://doi.org/10.5281/zenodo.7437689}.
The data is available in the R package \texttt{ReplicationSuccess} (available on
CRAN). Further information can be found on the corresponding help page (with the
command \texttt{?RProjects}).

\section*{Acknowledgments}
We acknowledge helpful and constructive comments by the editor and a referee on
an earlier version of this article.

### 2022-12-14 paper2.tex
formatting and reproducibility

\begin{figure}[!htb]
  \centering
%% first attempt
\begin{tikzpicture}[node distance = 5em, thick]
  % nodes %
  \node[font = \large] (data) {$f(\text{data} \,|\, \theta)$};
  \node[font = \large] (prior) [left=7em of data] {$f(\theta)$};
  \node[font = \large] (post) [right=7em of data] {$f(\theta \,|\, \text{data})$};
  \node[text width=10em,text centered] (RBinference) [below of=prior] {Reverse-Bayes inference};
  \node[text width=10em, text centered] (FBinference) [below of=post] {Forward-Bayes inference};

@@

The bottom-right plot in Figure~\ref{fig2:dcomparison} shows the success region
for the recalibrated sceptical $p$-value. We see that increasing the precision
of the replication study lowers the required minimum relative effect estimate
$\dmin$ as for all other methods. Similarly, as with the sceptical Bayes factor,
$\dmin$ of the sceptical $p$-value cannot be pushed arbitrarily close to zero.
However, its limiting minimum relative effect estimate in $c$
($\lim_{c \to \infty}\dmin$) is smaller than the one from the sceptical Bayes
factor when $\minBF_{o} < 1/5.6$, while for
$\minBF_{o} > 1/5.6$ it is the other way around. So for more
convincing original studies the sceptical $p$-value is less stringent than the
sceptical Bayes factor. Due to the recalibration, the sceptical $p$-value also
allows replication success when the $\minBF_{o} > \gamma$. This is visible in
the bottom-right plot of Figure~\ref{fig2:dcomparison} where the success region
has no cut-off at $\minBF_{o} = \gamma = 1/3$, unlike the two-trials rule and
the sceptical Bayes factor.

@@

\section{Application}
\label{sec2:applications}
The following section will illustrate application of the sceptical Bayes factor
using data from the \emph{Social Sciences Replication Project}
\citep{Camerer2018}, provided in Table \ref{tab:ssrp}. Effect estimates were
reported on the correlation scale ($r$), which is why we applied the Fisher
$z$-transformation $\hat{\theta} = \text{tanh}^{-1}(r)$. This leads to the
transformed estimates having approximate variance
$\Var(\hat{\theta}) = 1/(n - 3)$ \citep{Fisher1921}, so the relative variance
$c$ is roughly the ratio of the replication to the original study sample size
$c \approx n_{r}/n_{o}$.

@@

\section*{Funding}
This work was supported by the Swiss National Science Foundation (project number
189295, \url{http://p3.snf.ch/Project-189295}). The funder had no role in study
design, data collection and analysis, decision to publish, or preparation of the
manuscript.

>>>>

\begin{figure}[!htb]
  \centering
%% first attempt
\begin{tikzpicture}[node distance = 5em, thick]
  % nodes %
    \node[text width=5em, text centered] (data) {Likelihood $f(\text{data} \,|\, \theta)$};
    \node[text width=3em, text centered] (prior) [left=6.5em of data] {Prior $f(\theta)$};
    \node[text width=5em, text centered] (post) [right=5em of data] {Posterior $f(\theta \,|\, \text{data})$};
  \node[text width=10em,text centered] (RBinference) [below of=prior] {Reverse-Bayes inference};
  \node[text width=10em, text centered] (FBinference) [below of=post] {Forward-Bayes inference};

@@

The bottom-right plot in Figure~\ref{fig2:dcomparison} shows the success region
for the recalibrated sceptical \mbox{$p$-value}. We see that increasing the
precision of the replication study lowers the required minimum relative effect
estimate $\dmin$ as for all other methods. Similarly, as with the sceptical
Bayes factor, $\dmin$ of the sceptical $p$-value cannot be pushed arbitrarily
close to zero. However, its limiting minimum relative effect estimate in $c$
($\lim_{c \to \infty}\dmin$) is smaller than the one from the sceptical Bayes
factor when $\minBF_{o} < 1/5.6$, while for $\minBF_{o} > 1/5.6$ it is the other
way around. So for more convincing original studies the sceptical $p$-value is
less stringent than the sceptical Bayes factor. Due to the recalibration, the
sceptical $p$-value also allows replication success when the
$\minBF_{o} > \gamma$. This is visible in the bottom-right plot of
Figure~\ref{fig2:dcomparison} where the success region has no cut-off at
$\minBF_{o} = \gamma = 1/3$, unlike the two-trials rule and the sceptical Bayes
factor.

@@

\section{Application}
\label{sec2:applications}
The following section will illustrate application of the sceptical Bayes factor
using data from the \emph{Social Sciences Replication Project}
\citep{Camerer2018}, provided in Table \ref{tab:ssrp}. Effect estimates were
reported on the correlation scale ($r$), which is why we applied the Fisher
$z$-transformation $\hat{\theta} = \text{tanh}^{-1}(r)$. This leads to the
transformed estimates having approximate variance
\mbox{$\Var(\hat{\theta}) = 1/(n - 3)$} \citep{Fisher1921}, so the relative
variance $c$ is roughly the ratio of the replication to the original study
sample size $c \approx n_{r}/n_{o}$.

@@

% \section*{Funding}
% This work was supported by the Swiss National Science Foundation (project number
% 189295, \url{http://p3.snf.ch/Project-189295}). The funder had no role in study
% design, data collection and analysis, decision to publish, or preparation of the
% manuscript.

### 2022-12-14 paper3.tex
formatting and reproducibility

\section*{Acknowledgments}
This work was supported by the Swiss National Science Foundation (\#189295). The
funder had no role in study design, data collection, data analysis, data
interpretation, decision to publish, or preparation of the manuscript. We thank
\citet{Protzko2020} for publicly sharing their data. We thank Charlotte
Micheloud and Angelika Stefan for helpful comments on drafts of the manuscript.
Our acknowledgment of these individuals does not imply their endorsement of this
article.

>>>>

\section*{Acknowledgments}
% This work was supported by the Swiss National Science Foundation (\#189295). The
% funder had no role in study design, data collection, data analysis, data
% interpretation, decision to publish, or preparation of the manuscript.
We thank \citet{Protzko2020} for publicly sharing their data. We thank Charlotte
Micheloud and Angelika Stefan for helpful comments on drafts of the manuscript.
Our acknowledgment of these individuals does not imply their endorsement of this
article.

### 2022-12-14 paper5.tex
formatting
formatting and reproducibility

Assume, as per Sondhi et al., that both the likelihood of an effect estimate
$\hat{\theta}$ (the ``data'') and the prior of the underlying effect size
$\theta$ are represented by normal distributions
$\hat{\theta}\given \theta \sim \Nor(\theta, \sigma^{2})$ and
$\theta \sim \Nor(\mu, \tau^{2})$, with the latter evidence coming either from
pre-existing insight/studies or from a subsequent replication. Bayes's Theorem
then implies a posterior distribution
$\theta \given \hat{\theta} \sim \Nor(\mu_{p}, \tau^{2}_{p})$ whose mean and
variance satisfy
\begin{align*}
  &\frac{\mu_{p}}{\tau^{2}_{p}} = \frac{\hat{\theta}}{\sigma^{2}} + \frac{\mu}{\tau^{2}}&
  &\text{and}&
  &\frac{1}{\tau^{2}_{p}} = \frac{1}{\sigma^{2}} + \frac{1}{\tau^{2}}&
\end{align*}
Sondhi et al. further assume that $\tau^{2} = \sigma^{2}$, that is, the prior
variance $\tau^{2}$ is equal to the data variance $\sigma^{2}$ which itself is
equal to the squared (known) standard error $\sigma$ of the effect estimate
$\hat{\theta}$. It then follows that the posterior mean is the mean of the data
and the prior mean, and that the posterior variance is half the data variance
\begin{align}
  &\mu_{p} = \frac{\hat{\theta} + \mu}{2}&
  &\text{and}&
  &\tau^{2}_{p} = \frac{\sigma^{2}}{2}&
  \label{eq5:varconstraints}
\end{align}

@@

\section*{Software and data}
Summary statistics on the case study were taken from \citet{Sondhi2021}. The
code to reproduce our analyses is available at
\url{https://github.com/SamCH93/BAEcomment}. A snapshot of the Git repository at
the time of writing is archived at \url{https://doi.org/10.5281/zenodo.XXXXXX}.

\section*{Acknowledgments}
We thank two anonymous referees and the third referee Riko Kelter for their
helpful suggestions. Financial support from the Swiss National Science
Foundation (Project \#189295) is gratefully acknowledged. The funder had no role
in study design, data collection, data analysis, data interpretation, decision
to publish, or preparation of the manuscript.

>>>>

Assume, as per Sondhi et al., that both the likelihood of an effect estimate
$\hat{\theta}$ (the ``data'') and the prior of the underlying effect size
$\theta$ are represented by normal distributions
$\hat{\theta}\given \theta \sim \Nor(\theta, \sigma^{2})$ and
$\theta \sim \Nor(\mu, \tau^{2})$, with the latter evidence coming either from
pre-existing insight/studies or from a subsequent replication. Bayes's Theorem
then implies a posterior distribution
\mbox{$\theta \given \hat{\theta} \sim \Nor(\mu_{p}, \tau^{2}_{p})$} whose mean
and variance satisfy
\begin{align*}
  &\frac{\mu_{p}}{\tau^{2}_{p}} = \frac{\hat{\theta}}{\sigma^{2}} + \frac{\mu}{\tau^{2}}&
  &\text{and}&
  &\frac{1}{\tau^{2}_{p}} = \frac{1}{\sigma^{2}} + \frac{1}{\tau^{2}}&
\end{align*}
Sondhi et al. further assume that $\tau^{2} = \sigma^{2}$, that is, the prior
variance $\tau^{2}$ is equal to the data variance $\sigma^{2}$ which itself is
equal to the squared (known) standard error $\sigma$ of the effect estimate
$\hat{\theta}$. It then follows that the posterior mean is the mean of the data
and the prior mean, and that the posterior variance is half the data variance
\begin{align}
  &\mu_{p} = \frac{\hat{\theta} + \mu}{2}&
  &\text{and}&
  &\tau^{2}_{p} = \frac{\sigma^{2}}{2}&
  \label{eq5:varconstraints}
\end{align}

@@

\section*{Software and data}
Summary statistics on the case study were taken from \citet{Sondhi2021}. The
code to reproduce our analyses is available at
\url{https://github.com/SamCH93/BAEcomment}. A snapshot of the Git repository at
the time of writing is archived at \url{https://doi.org/10.5281/zenodo.7437722}.

\section*{Acknowledgments}
We thank two anonymous referees and the third referee Riko Kelter for their
helpful suggestions.%  Financial support from the Swiss National Science
% Foundation (Project \#189295) is gratefully acknowledged. The funder had no role
% in study design, data collection, data analysis, data interpretation, decision
% to publish, or preparation of the manuscript.

### 2022-12-14 preface.tex
formatting and reproducibility

First and foremost I want to thank my supervisor Leo for giving me the
opportunity to do this PhD, for showing me an open-minded and pragmatic approach
to statistics, and for giving me the freedom to explore and develop into an
independent researcher. I also want to thank the other two members of my PhD
committee, Guido and Reinhard, for always providing excellent advice and being
great collaborators. Another thanks goes to Robert Matthews who also is a great
collaborator and without whom this PhD project would never exist as it was him
who resurrected the reverse-Bayes approach from the dead almost twenty years
ago. Furthermore, I want to thank Eric-Jan Wagenmakers for reviewing this thesis
and for giving me the opportunity to do a very interesting and productive six
months research stay in Amsterdam.

I also want to thank my friends and colleagues from the Epidemiology,
Biostatistics and Prevention Institute from the University of Zurich (in
alphabetical order): Ainesh, Alexandra, Annina, Charlotte, Babette, Bálint,
Beate, Beni, Dafne, Dominik, Eveline, Eva, Franscesca, Felix, Julia, Klaus,
Kelly, Lucas, Lisa, Luisa, Goscha, Manuela, Monika, Muriel, Manja, Maria,
Marielena, Martin, Mina, Nadja, Ruedi, Rachel, Sandra, Sona, Steffi, Tala,
Torsten, and Ulrike. Another thanks goes to my friends from the Department of
Psychological Methods from the University of Amsterdam (in alphabetical order):
Adam, Alexander, Alexandra, Alessandra, Alejandro, Angelika, Bruno, Don,
František, Frederik, Jason, Johnny, Joris, Jill, Julia, Lukas, Maarten,
Michelle, Nora, Omid, Quentin, René, Serjan, Suzanne, and Ting. I also want to
thank my good friends from outside of academia (in alphabetical order): Chronis,
Dani, Eleftheria, Flo, Fabi, Giuachin, Mirela, and Peter. A special thanks goes
to Ada. Finally, I thank my family: Beni, Christa, Elisabeth, Fabian, Harry,
Markus, Maja, and Noemi for their support.

>>>>

First and foremost I want to thank my supervisor Leo for giving me the
opportunity to do this PhD, for showing me an open-minded and pragmatic approach
to statistics, and for giving me the freedom to explore and develop into an
independent researcher. I also want to thank the other two members of my PhD
committee, Guido and Reinhard, for always providing excellent advice and being
great collaborators. Another thanks goes to Robert Matthews who also is a great
collaborator and without whom this PhD project would never exist as it was him
who resurrected the reverse-Bayes approach from the dead almost twenty years
ago. Furthermore, I want to thank Eric-Jan Wagenmakers for giving me the
opportunity to do a very interesting and productive six months research stay in
Amsterdam.

I also want to thank my friends and colleagues from the Epidemiology,
Biostatistics and Prevention Institute from the University of Zurich (in
alphabetical order): Ainesh, Alexandra, Annina, Charlotte, Babette, Bálint,
Beate, Beni,Eveline, Eva, Franscesca, Felix, Julia, Klaus, Kelly, Lucas, Lisa,
Luisa, Goscha, Manuela, Monika, Muriel, Manja, Maria, Marielena, Nadja, Ruedi,
Rachel, Sandra, Sona, Steffi, Torsten, and Ulrike. Another thanks goes to my
friends from the Department of Psychological Methods from the University of
Amsterdam (in alphabetical order): Adam, Alexander, Alexandra, Alessandra,
Angelika, Bruno, Don, František, Frederik, Jason, Johnny, Joris, Jill, Lukas,
Maarten, Michelle, Nora, Omid, Quentin, René, Serjan, Suzanne, and Ting. I also
want to thank my good friends from outside of academia (in alphabetical order):
Chronis, Dani, Eleftheria, Flo, Fabi, Giuachin, Mirela, and Peter. A special
thanks goes to Ada. Finally, I thank my family: Beni, Christa, Elisabeth,
Fabian, Harry, Markus, Maja, and Noemi for their support.

### 2022-12-14 thesis.Rnw
one-sided sceptical p
formatting and reproducibility

%% load the hyperref package
\usepackage{hyperref}
\hypersetup{
  bookmarksdepth = 2,  % otherwise same depth as TOC (only chapters)
  colorlinks = {true},
  linkcolor = {black},
  breaklinks = {true},
  citecolor = {Blue},
  urlcolor = {Blue},
  pdftitle = {Reverse-Bayes Methods for Replication Studies and Beyond},
  pdfauthor = {Samuel Pawel},
  pdfsubject = {},
  pdfpagemode = {UseOutlines}
}

@@

\addtocontents{toc}{\bigskip}
\addtocontents{toc}{\bigskip}
\addtocontents{toc}{%
  \protect\vspace{2ex}
  \textbf{\textsf{Integrity in methodological research}}\par}
\addtocontents{toc}{%
  \protect\vspace{-2ex}
  \par\noindent\rule{\textwidth}{0.4pt}\par}

@@

% ==============================================================================
% APPENDIX
% ==============================================================================

% \appendix
% \renewcommand{\chaptername}{Appendix}
% \paperchapter{%
% Multivariate reverse-Bayes analysis
% \label{app:multiRB}
% }{%
%  Samuel Pawel
% }{}

% \paperchapter{%
% Reverse-Bayes asssessment of multiple replications
% \label{app:multipleRB}
% }{%
%  Samuel Pawel
% }{}

>>>>

%% load the hyperref package
\usepackage{hyperref}
\hypersetup{
  bookmarksdepth = 2,  % otherwise same depth as TOC (only chapters)
  colorlinks = {true},
  linkcolor = {black},
  breaklinks = {true},
  citecolor = {Blue},
  urlcolor = {Blue},
  pdftitle = {Reverse-Bayes Methods for Replication Studies},
  pdfauthor = {Samuel Pawel},
  pdfpagemode = {UseOutlines}
}

@@

\addtocontents{toc}{\bigskip}
\addtocontents{toc}{\bigskip}
\addtocontents{toc}{%
  \protect\vspace{2ex}
  \textbf{\textsf{Meta-scientific perspectives on methodological research}}\par}
\addtocontents{toc}{%
  \protect\vspace{-2ex}
  \par\noindent\rule{\textwidth}{0.4pt}\par}

@@
